---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidseasonality

<!-- badges: start -->
<!-- badges: end -->

The goal of `covidseasonality` package is to improve the accessibility and readability of its corresponding Shiny app. 

## Installation

<!-- You can install the released version of covidseasonality from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("covidseasonality") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-brenwin1")
```
## Example

This is a basic example what the package includes  

inbuilt datasets with countries in each hemisphere 
```{r dataset-eg}
library(covidseasonality)
library(tibble)

Northern_hemis # countries in the Northern Hemisphere
```

Takes data frame and plots daily cases against date. With shaded area indicating winter months.
```{r plot-eg}
library(dplyr)
join_data <- left_join(filter(covidseasonality::covid_data, country == "Australia"), 
                       filter(covidseasonality::world, region == "Australia"), 
                       by = c("country" = "region"))

join_data %>% 
  filter(country == "Australia") %>% 
  plot_countries_hemis()
```

